Appendix

### 2017-10-24 appendix/appendix.Rmd
WIP

```{r}
library(nimble)
library(hrbrthemes)
library(ggthemes)
library(tidyverse)
ggplot2::theme_set(hrbrthemes::theme_ipsum())
```

@@

```{r}
tipping <- read_csv("appendix/tipping.csv")

>>>>

```{r}
library(nimble)
library(hrbrthemes)
library(ggthemes)
library(RcppRoll)
library(regimeshifts) ## devtools::install_github("cboettig/regimeshifts")
library(tidyverse)
ggplot2::theme_set(hrbrthemes::theme_ipsum())
```

@@

```{r}
tipping <- read_csv("tipping.csv")
